---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# PRU Atlas

<!-- badges: start -->
[![R build status](https://github.com/euctrl-pru/pruatlas/workflows/R-CMD-check/badge.svg)](https://github.com/euctrl-pru/pruatlas/actions)
[![R build status](https://github.com/euctrl-pru/pruatlas/workflows/pkgdown/badge.svg)](https://github.com/euctrl-pru/pruatlas/actions)
<!-- badges: end -->


The `pruatlas` package provides helpers for generating maps of interest for PRU publications.

This is still Work In Progress.

There are both high and low level facilities.
For an example of a high level helper, the code for plotting a map of the
French country FIR is just a one-liner:

```{r lf-fir, message=FALSE}
library(sf)
library(pruatlas)
plot_country_fir("LF", "France")
```

Lower level functions or datasets include for example `countries50m`, the Simple Feature
for the whole world countries or `extent_fir()` to calculate the bounding box of
a country FIR.

Useful functions are:

* `plot_country_fir()`
* `plot_country_ansp()`

The package contains the following aviation GIS datasets (for CFMU AIRAC 406, see below):

* `firs_nm_406`: the FIR's as defined/used by EUROCONTROL's Network Manager
* `ansps_ace_406`: the ANSP's as defined/used in ACE Benchmarking Report

(CFMU) AIRAC 406, a.k.a. [AIRAC](https://ansperformance.eu/acronym/airac/) `1512`,
spans the 28-day interval 2015-11-12 UTC--2015-12-10 UTC.

If you need polygons in different AIRAC's that the one in the package and have access
to EUROCONTROL DB, you can have a look at the scripts in the `data-raw` directory. 
For example `export_nm_fir_geojson.R` or `export_ace_ansp_geojson.R` allow for
exporting FIR's or ANSP's to GeoJSON which can be read as {`sf`} features
via `sf::read_sf()`.


# Installation

`Pruatlas` is still in early development and it is only available on GitHub.
It relies and uses the functionality from the `sf` package and this relies
on a working installation of GDAL, see the `sf` installation instructions
for directions.

In order to install `pruatlas` you need to run:

```{r dev-install, eval=FALSE}
library(remotes)
install_github("euctrl-pru/pruatlas")
```

# To Do's

- [ ] implement similar facilities as FIR's/ANSP's for Elementaty Sectors (ES's)
  in order to be able to plot ACC's
- [ ] include `export_<airspace_type>` in the package API rather than as scripts
  for the package datasets
- [ ] extract style from plot functions and make it a better theme
