---
output: github_document
published: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# PRU Atlas

The `pruatlas` package provides helpers for generating maps of interest for PRU pubblications.

This is still WIP.

There are both high and low level facilities.
For an example of a high level helper, the code for plotting a map of the
French country FIR is just a one-liner:

```{r lf-fir, message=FALSE}
library(pruatlas)
plot_country_fir("LF", "France")
```

Lower level functions or datasets include for example `ctrys50m`, the Simple Feature
for the whole wolrd countries or `extent_fir()` to calculate the bounding box of
a country FIR.


# Installation

`Pruatlas` is still in early development and it is only available on GitHub.
It relies and uses the functionality from the `sf` package and this relies
on a working installation of GDAL, see the `sf` installation instructions
for directions.
Also note that support for Simple Feature is still in development in `ggplot2`:
you need to install from GitHub untill officially released (sometimes in May 2017.)

In order to install `pruatlas` you need to run:

```{r dev-install, eval=FALSE}
library(devtools)
install_github("euctrl-pru/pruatlas")
```
